Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2020-04-30 paper2_JNLS/Referee Reports/Ref2Response/Ref2.tex
NM

% COMMENT
\noindent
\comment{A nice paper with agreement between theory and experiments, and novel new results.
}
\begin{itemize}
\item We thank the referee for these positive remarks.
\end{itemize}

% COMMENT 1
\noindent
\comment{
Use of qualitative adjectives where a quantitative description may be better:
Pg 1 Ln 39: spectacular
Pg 17 Ln 17: intriguing
Pg 18 Ln 36: modest
Pg 19 Ln 37: roughly
Pg 20 Ln 42: remarkably}

\begin{itemize}
\item We have corrected these.
\end{itemize}

@@

\begin{itemize}
\item Yes
\end{itemize}

% COMMENT 3
\noindent
\comment{Section 4.1 refers to Figure 3(b). If you increase N, with the transfer function become eventually collapse to one single curve? If so or indeed if not, why choose the N and Lambda in this range?}

@@

>>>>

% COMMENT
\noindent
\comment{A nice paper with agreement between theory and experiments, and novel new results.} \\

\noindent
We thank the referee for these positive remarks. \\ \\

% COMMENT 1
\noindent
\comment{
Use of qualitative adjectives where a quantitative description may be better: \\
Pg 1 Ln 39: spectacular \\
Pg 17 Ln 17: intriguing \\
Pg 18 Ln 36: modest \\
Pg 19 Ln 37: roughly \\
Pg 20 Ln 42: remarkably} \\

\noindent
We have replaced the majority of these descriptors with more quantitative ones. In particular:
\begin{itemize}
\item The term `spectacular fashion' in the abstract was changed to `convincing evidence'.
\item The word `modest' on page 18 was replaced with `intermediate'.
\item The word `roughly' (appearing in several places in the original manuscript) was either replaced by `approximately' or else removed.
\item The phrase `captures the trend remarkably well' on page 20 was changed to `captures the trend closely'.
\item We have kept `intriguing' on page 17 as we believe it to be an appropriate use of the word.
\end{itemize}
\hphantom \\

@@

\begin{itemize}
\item As can bee seen in Fig. 2 (b) and (c), the location of the peak is indeed insensitive to driving amplitude to within experimental error (the level of which can be estimated by the noise in the data). Accordingly, we have replaced `appears insensitive' to simply `is insensitive'.
We had initially used the word `appears' to encourage the reader to view the figure and see for themselves. However, we now see the referee's point that this word may introduce some uncertainty in the reader's mind and have thus made the change.
\end{itemize}

% COMMENT 3
\noindent
\comment{Section 4.1 refers to Figure 3(b). If you increase $N$, with the transfer function become eventually collapse to one single curve? If so or indeed if not, why choose the $N$ and $\Lambda$ in this range?}

\begin{itemize}
\item This is a great question....
\end{itemize}

@@

\begin{itemize}
\item We have added  labels for the colourbars in Fig. 6.
\end{itemize}
